{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-03-06 documents/brillouin_pulse_math.tex
More work on writing, need to add pulse counts
Removed README disclaimer

The loss and refractive index can be obtained from a four term Cole-Cole model\cite{gabriel1996compilation}\footnote{implemented in\ghfile{/electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py}}. We used parameters from the IT.IS Foundation tissue database\cite{Tissue2018a}.

@@

where $\int e^{j \omega t} d\omega$ is the inverse fourier transform. At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020}, or substitute

@@

Note the ni specifically in the complex conjugate!

@@

However, a maximum absolute value constraint produces fantastic results.

>>>>

The loss and refractive index can be obtained from a four term Cole-Cole model\cite{gabriel1996compilation}\footnote{implemented in\ghfile{/electronics/simple_fdtd/fdtd_PCB_extensions/fdtd_PCB_extensions/tissue.py}}. We used parameters from the IT.IS Foundation tissue database\cite{Tissue2018a}. IT.IS Foundation computational phantom 'duke V3.0' was used, \cite{Duke2014}.

@@

where $\int e^{j \omega t} d\omega$ is the inverse fourier transform. At this point, you could choose to perform a second integral over the time-domain Greens function solution to the harmonic oscillator\cite{Complex2020} - or straightforwardly integrate over the frequency-domain Greens function.

@@

\footnote{Note the ni specifically in the complex conjugate!}

@@

However, a maximum absolute value constraint appears to produce fantastic results.

### 2021-03-06 documents/summary.tex
Removed README disclaimer

It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could tend towards only the most abstruse and difficult to explain false-positive results.

@@

\end{multicols}
\begin{autem}
	autem, discuss\\
	At the risk of seeming a fool, what is the correct metric for the charge quantity being discussed? We are interested in the stress produced by a certain arbitrary distribution of charge. Assuming a spherically symmetric virus composed of two charged shells, there is no intrinsic dipole moment. Polarizability or induced dipole moment are not obviously relevant; stress could be produced in an extremely stiff structure with no electron mobility. The virion has little net charge. Multipole expansions are not clearly relevant.
\end{autem}
\begin{multicols}{1}
From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will likely require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}.

@@

Accurately modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms simultaneously with fatigue from atomic dislocations\cite{Physical2010} and reactive oxidation effects poses a significant computational and theoretical hassle, which has far exceeded our capabilities.

@@

Parameterizing coarse bead-spring models based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009} is another technique. In this case, DNA/RNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}. Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}. Finite-element analysis \cite{Finite2008}

Coupling finite-element and Poisson-Boltzmann\cite{Electrostatic2020a}.

@@

Early albanese with mm used vircator diodes.

What quantity is referred to; induced dipole due to polarization or ionic.

T4r was selected for biosafety reasons, and because of the large amount of structural data available. T4\cite{History1995} does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}. Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}, or lipid liposomes. Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.

Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}. We encountered one problem removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult. However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory. This likely does not lead to DNA precipitation because of the lack of salt.

When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds 100 atm \cite{Osmotic2003}. By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa

@@

PMT dark counts and ambient light were removed by synchronous photon counting - add when light is on, subtract when light is off.  This cannot be done with luminescence. Further filtering could be done by fluorescence lifetime discrimination.

@@

Nephelometry (right-angle light scatter detection) and turbidimetry (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E. coli cultures 1.5 mL. Turbidimetry\cite{Fast2019} Impedimietric In addition, removing the necessitating

E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism. A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated, as described in\cite{rapid2014}. One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use. Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient. The detergent could perhaps be removed with BioBeads if this is desired.

@@

A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.05 mm waveguide.

@@

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca. A special thanks to the dedicated authors that develop and maintain these tools, and especially to those who choose not to put them behind a paywall.

>>>>

\footnote{It is interesting to consider that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could unintentionally tend towards a literature populated with only the most abstruse and difficult to explain false-positive results.}

@@

\end{multicols}
\begin{autem}
	autem, discuss\\
	At the risk of seeming a fool, what is the most useful metric for the charge quantity being discussed? We are interested in the stress produced by a certain arbitrary distribution of charge. Assuming a spherically symmetric virus composed of two charged shells, there is no intrinsic dipole moment. Polarizability or induced dipole moment are not obviously relevant; stress could be produced in an extremely stiff structure with no electron mobility. The virion has little net charge. Multipole expansions are not clearly relevant.
\end{autem}
\begin{multicols}{1}
From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will likely require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}.

@@

Accurately modelling this sort of multi-scale inactivation mechanism involving the collective motion of some $10^9$ atoms, possibly simultaneously with fatigue from atomic dislocations\cite{Physical2010} and reactive oxidation effects, poses a significant computational and theoretical hassle, which has far exceeded our capabilities.

@@

Parameterizing coarse bead-spring models based on all-atom simulations of small capsid segments or proteins \cite{Elucidating2009} is another technique. In this case, DNA/RNA can be represented by homogeneous beads restrained by Lennard-Jones forces \cite{Communication2013}. Mechanically reasonable coarse-grained models have recently been published for SARS-NCoV-2\cite{Multiscale2020}. Finite-element analysis in biology is also somewhat common \cite{Finite2007}; coupled finite-element and Poisson-Boltzmann\cite{Electrostatic2020a} seems particularly effective.

@@

%Early albanese with mm used vircator diodes.

E. coli phage T4r was selected for biosafety reasons, and because of the large amount of experience\cite{History1995} and structural data available. T4 does not have a nucleocapsid; the charge distribution is likely much stronger than other RNA-like viruses Phi 6\footnote{Naming organisms with greek letters makes literature review somewhat more difficult, because many search engines do not support Unicode.}. Some more useful surrogates may include Pseudomonas Phi 6\cite{Selection2017}, the lipid-bearing PM2, PRD1 or PR4\cite{Lipidcontaining1979} if the outer protein capsid is dissolved\cite{Bacteriophage2002}, \cite{Dissociation1993}; or synthetic lipid liposomes. Certain phages also allow efficient concentration without ultracentrifuge, either by PEG precipitation\cite{Rapid1970} and settling, or via VIRADEL\cite{GROWTH}\cite{Chemical1982}\cite{highly1988}\cite{AdsorptionElution1989}, by altering the zeta potential of a syringe filter.

Custom single-lipid liposome surrogates appear to be relatively easy to produce and fill with a DNA tracer by sonication and dehydration\cite{Encapsulation1982}\cite{OPTIMIZATION2017}\cite{Liposome2014}. We encountered one problem in removing unencapsulated DNA, which typically requires ultracentrifugation as precipitation of liposomes is difficult. However, \cite{novela} appear to demonstrate that ethanol extraction is satisfactory - we have not tested this. This likely does not lead to DNA precipitation because of the lack of salt.

When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds about 100 atm \cite{Osmotic2003}. By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa

@@

PMT dark counts and ambient light were removed by synchronous photon counting\cite{Measurement1966} - add when light is on, subtract when light is off.  This cannot be done with luminescence. Further filtering could be done by fluorescence lifetime discrimination.

@@

%Nephelometry (right-angle light scatter detection) and turbidimetry (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E. coli cultures 1.5 mL. Turbidimetry\cite{Fast2019} Impedimietric In addition, removing the necessitating

E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism. A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated, as described in\cite{rapid2014}. One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use. Perhaps the detergent is not effective on bacteria, or the paper substrate that was used in the previous work was sufficient to bind the detergent. The detergent could perhaps be removed with BioBeads if this is desired.

@@

A thin layer of silicone conformal coating was applied to the 0.2 mm waveguide to avoid the copper ion artifact, but this could not be done on the 0.03 mm waveguide.

@@

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca/qucs\cite{Modeling2010}. A special thanks to the dedicated authors that develop and maintain these tools, and especially to those who choose not to put them behind a paywall.
